text

### 2016-09-03 forgerard.tex
more edits

In this article we use the idea that spectral indicators carry information on intrinsic supernova colors,
and allow for the possibility of there being two further color parameters, one intrinsic and the other
extrinsic.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
\S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
supernova SN2014J that has been previously identified as having extreme color properties.
We finish with conclusions in \S\ref{conclusions:sec}.

@@

%A representative example is given by the matrix comprised by the average of each element in the Monte Carlo chain.
%For $UBVRI$ the matrix is
%\begin{equation}
%\begin{pmatrix}
%0.0050 & 0.0026 & 0.0017 & 0.0014 & 0.0009 \\
%0.0026 & 0.0034 & 0.0032 & 0.0026 & 0.0011 \\
%0.0017 & 0.0032 & 0.0047 & 0.0041 & 0.0029 \\
%0.0014 & 0.0026 & 0.0041 & 0.0042 & 0.0035 \\
%0.0009 & 0.0011 & 0.0029 & 0.0035 & 0.0050
% \end{pmatrix}.
% \end{equation}
% In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
%\begin{equation}
%\begin{pmatrix}
%0.0064 & 0.0025 & -0.0004 & -0.0010 \\
%0.0025 & 0.0018 & -0.0000 & 0.0003 \\
%-0.0004 & -0.0000 & 0.0007 & 0.0011 \\
%-0.0010 & 0.0003 & 0.0011 & 0.0039
%  \end{pmatrix}.
% \end{equation}
% The $B-V$ and $V-R$ colors have small standard deviations of  0.04 mag and 0.03 mag with no correlation.  The
% residuals not accounted by the
% model are stronger in the $U-V$ and $V-I$ bands.

@@

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.

@@

\section{Conclusions}
\label{conclusions:sec}

Large $E(B-V)$ does not mean extinction.

@@

$R^F_V=2.5$.

@@

>>>>

In this article we use the idea that spectral indicators carry information on intrinsic supernova colors,
and allow for the possibility of there being two further color parameters, one intrinsic and the other
extrinsic.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
\S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
supernova SN2014J that has been previously identified as having extreme color properties.
We finish with a discussion of our findings in \S\ref{discussion:sec}.

@@

@@

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.
The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: selecting new Cholesky factors baased
on their distributions generally will not satisfy the condition of representing a correlation matrix.  
As a representation of a typical posterior draw of $C_c$ we present a matrix that element-by-element
is the mean of all covariance realizations.
For $UBVRI$ the matrix is
\begin{equation}
\begin{pmatrix}
0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
-0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
-0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
 \end{pmatrix} \text{mag}^2.
 \end{equation}
Similarly the typical color covariance, in terms of colors $U-V$, $B-V$, $V-R$, and $V-I$, can
be expressed as having standard deviations $(0.066 , 0.033 , 0.022 , 0.050)$ mag with
 correlations
 \begin{equation}
\begin{pmatrix}
1.000 & 0.634 & -0.256 & -0.300 \\
0.634 & 1.000 & -0.203 & 0.032 \\
-0.256 & -0.203 & 1.000 & 0.604 \\
-0.300 & 0.032 & 0.604 & 1.000
  \end{pmatrix}.
 \end{equation}

@@

\section{Discussion}
\label{discussion:sec}
The model favors spectral features as indicating supernova magnitude and color, and the existence of an internal supernova parameter
that affects colors, in addition to external (dust) colors.

The extrinsic dust gives $R^F_V=2.5$. Intrinsic cannot be associated with dust.

Could affect distance determinations.  Large $E(B-V)$ does not mean extinction.

@@

Getting $R_V=1.5$ not surprising.

@@

Room for more color effects.  Dispersion in $R_V$.   With negative and positive correlations can't be explained by dust.

Anti-connection between $EW(Ca)$ and $v_{Si}$.  Intermediate mass
